A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-03 final project/Manuscript_Corey.RMD
Added some simple correlation plots
I just added some simple correlation plots also let me know if you want to keep the variables names as the acronyms I just did it so they are more readable for the correlation plots

---
title             : "A Logistic Regression Approach to CoIL Challenge 2000"
shorttitle        : " "
author            : "Corey Arnouts, Adam Douglas, Jason Givens-Doyle, Michael Silva"
affiliation       : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output: 
  word_document:
    reference_docx: word-template.docx
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
  html_document: default
---

@@

>>>>

---
title             : "A Logistic Regression Approach to CoIL Challenge 2000"
shorttitle        : " "
author            : "Corey Arnouts, Adam Douglas, Jason Givens-Doyle, Michael Silva"
affiliation       : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  -->
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output: 
  html_document: default
  word_document:
    reference_docx: word-template.docx
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
---

@@

# Analysis

```{r}
colnames(df)<-c("Customer_Subtype","Number_of_houses", "Avg_size_household", "Avg_age", "Customer_main_type", "Roman_catholic", "Protestant","Other_religion", "No_religion", "Married", "Living_together", "Other_relation", "Singles", "Household_without_children", "Household_with_children", "High_level_education", "Medium_level_education", "Lower_level_education", "High_status", "Entrepreneur", "Farmer", "Middle_management", "Skilled_labourers", "Unskilled_labourers", "Social_class_A", "Social_class_B1", "Social_class_B2", "Social_class_C", "Social_class_D", "Rented_house", "Home_owners", "1_car", "2_cars", "No_car", "National_Health_Service", "Private_health_insurance", "Income_<_30.000", "Income_30-45.000", "Income_45-75.000", "Income_75-122.000", "Income_>123.000", "Average_income", "Purchasing_power_class", "Contribution_private_third_party_insurance", "Contribution_third_party_insurance_(firms)", "Contribution_third_party_insurane_(agriculture)", "Contribution_car_policies", "Contribution_delivery_van_policies", "Contribution_motorcycle/scooter_policies", "Contribution_lorry_policies", "Contribution_trailer_policies", "Contribution_tractor_policies", "Contribution_agricultural_machines_policies", "Contribution_moped_policies", "Contribution_life_insurances", "Contribution_private_accident_insurance_policies", "Contribution_family_accidents_insurance_policies", "Contribution_disability_insurance_policies", "Contribution_fire_policies", "Contribution_surfboard_policies", "Contribution_boat_policies", "Contribution_bicycle_policies", "Contribution_property_insurance_policies", "Contribution_social_security_insurance_policies", "Number_of_private_third_party_insurance", "Number_of_third_party_insurance_(firms)", "Number_of_third_party_insurane_(agriculture)", "Number_of_car_policies", "Number_of_delivery_van_policies", "Number_of_motorcycle/scooter_policies", "Number_of_lorry_policies", "Number_of_trailer_policies", "Number_of_tractor_policies", "Number_of_agricultural_machines_policies", "Number_of_moped_policies", "Number_of_life_insurances", "Number_of_private_accident_insurance_policies", "Number_of_family_accidents_insurance_policies", "Number_of_disability_insurance_policies", "Number_of_fire_policies", "Number_of_surfboard_policies", "Number_of_boat_policies", "Number_of_bicycle_policies", "Number_of_property_insurance_policies", "Number_of_social_security_insurance_policies", "Number_of_mobile_home_policy")

colnames(eval)<-c("Customer_Subtype","Number_of_houses", "Avg_size_household", "Avg_age", "Customer_main_type", "Roman_catholic", "Protestant","Other_religion", "No_religion", "Married", "Living_together", "Other_relation", "Singles", "Household_without_children", "Household_with_children", "High_level_education", "Medium_level_education", "Lower_level_education", "High_status", "Entrepreneur", "Farmer", "Middle_management", "Skilled_labourers", "Unskilled_labourers", "Social_class_A", "Social_class_B1", "Social_class_B2", "Social_class_C", "Social_class_D", "Rented_house", "Home_owners", "1_car", "2_cars", "No_car", "National_Health_Service", "Private_health_insurance", "Income_<_30.000", "Income_30-45.000", "Income_45-75.000", "Income_75-122.000", "Income_>123.000", "Average_income", "Purchasing_power_class", "Contribution_private_third_party_insurance", "Contribution_third_party_insurance_(firms)", "Contribution_third_party_insurane_(agriculture)", "Contribution_car_policies", "Contribution_delivery_van_policies", "Contribution_motorcycle/scooter_policies", "Contribution_lorry_policies", "Contribution_trailer_policies", "Contribution_tractor_policies", "Contribution_agricultural_machines_policies", "Contribution_moped_policies", "Contribution_life_insurances", "Contribution_private_accident_insurance_policies", "Contribution_family_accidents_insurance_policies", "Contribution_disability_insurance_policies", "Contribution_fire_policies", "Contribution_surfboard_policies", "Contribution_boat_policies", "Contribution_bicycle_policies", "Contribution_property_insurance_policies", "Contribution_social_security_insurance_policies", "Number_of_private_third_party_insurance", "Number_of_third_party_insurance_(firms)", "Number_of_third_party_insurane_(agriculture)", "Number_of_car_policies", "Number_of_delivery_van_policies", "Number_of_motorcycle/scooter_policies", "Number_of_lorry_policies", "Number_of_trailer_policies", "Number_of_tractor_policies", "Number_of_agricultural_machines_policies", "Number_of_moped_policies", "Number_of_life_insurances", "Number_of_private_accident_insurance_policies", "Number_of_family_accidents_insurance_policies", "Number_of_disability_insurance_policies", "Number_of_fire_policies", "Number_of_surfboard_policies", "Number_of_boat_policies", "Number_of_bicycle_policies", "Number_of_property_insurance_policies", "Number_of_social_security_insurance_policies", "Number_of_mobile_home_policy","doornik")

```

# Relationships Between PolicyTypes
```{r}

policies <- df[ , grepl( "policies" , names( df ) ) ]
policies <- policies[ , grepl( "Number" , names( policies ) ) ]

policies2 <-sub("Number_of_", "", colnames(policies))
policies3 <-sub("_policies", "", policies2)
policies4 <-sub("insurance", "", policies3)
policies5 <-sub("_", " ", policies4)
policies6 <-sub("_", " ", policies5)

colnames(policies)<- policies6

cordf <- df %>% select(Social_class_A,Average_income)

library(corrplot)
M <- cor(policies)
corrplot(M) #plot matrix

```

# Relationships Between Variables
```{r}
features <- df[ , !grepl( "policies" , names( df ) ) ]
features <- features[ , !grepl( "Number" , names( features ) ) ]
features <- features[ , !grepl( "Insurance" , names( features ) ) ]
features <- features[ , !grepl( "insurance" , names( features ) ) ]
features <- features[ , !grepl( "insurane" , names( features ) ) ]
#features <- features[ , grepl( "education|income|Income" , names( features ) ) ]

library(corrplot)
M <- cor(features)
corrplot(M,tl.cex = .5) #plot matrix

features <- df[ , !grepl( "policies" , names( df ) ) ]
features <- features[ , !grepl( "Number" , names( features ) ) ]
features <- features[ , !grepl( "Insurance" , names( features ) ) ]
features <- features[ , !grepl( "insurance" , names( features ) ) ]
features <- features[ , !grepl( "insurane" , names( features ) ) ]
features <- features[ , grepl( "education|income|Income" , names( features ) ) ]

library(corrplot)
M <- cor(features)
corrplot(M,tl.cex = .5) #plot matrix

```
